InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
finished gpt section

\subsubsection{Image generating models}
The first image generating model we us is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.

\subsubsection{Text generating models}

>>>>

\subsubsection{Image generating models}

\subsubsection{Text generating models}
We choose the GPT model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.

Radford et. al try to avoid this problem in a simple two step procedure:
\begin{enumerate}
	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
	\item Discriminative fine-tuning on every specific task.
\end{enumerate}

To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
